### 2022-07-11 README.Rmd
Ensured temp[late files operational, and all examples work. Production ready. No EWN.
Switched from hutils to codeutils. Worked on internal consistency. No EWN.

>>>>

* 2022-07-10 aMSE 0.0.10 Switched dependency from hutils to codeutils. re-added zone1 for S21 to the data sets. No EWN.

* 2022-07-10 aMSE 0.0.9 Added data sets to allow for examples and documentation to illustrate the conditioning and running of the MSE. Added adjustavrec as a function, nade a wrapper rnormz and rlnormz to enable zero variation while still using up a random number so the sequence was maintained. Ready for production work. No EWN.
